Assessing Phonon Properties of Shape Memory Alloys using Graph Neural Network Potentials

### 2023-12-19 src/tex/ms.tex
Calculation scripts good. Some plotting good. Added draft MD simulation script. New Calculator.

\begin{figure}[ht!]
    \script{PlotNiTiCohesiveEnergy.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_CohesiveEnergy.png}
        \caption{
          Comparison of predicted cohesive energy for respective ground-state structure and model.
        }
        \label{fig:ecoh}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotNiTiEOS.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_EOS_Comparison.png}
        \caption{
            The equation of state curves for different \ce{NiTi} structures for (a) Mutter (EAM) (b) Zhong (EAM) (c) M3GNet (d) CHGNet (e) MACE and (f) ALIGNN interatomic potentials. The x-axis is the ratio of the isotropic strained unit cell volume, $V$,  with respect to the ground-state unit cell volume, $V_o$.
        }
        \label{fig:eos}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \script{PlotNoStrainPhonons.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/B2_combined_models_phonon_bandstructures.png}
        \caption{
          Ground-state, no isotropic strain, Phonon bandstructure of B2 phase for all models. The Mutter and Zhong EAM potentials differ in that Mutter predicts no dynamic instability of the B2 phase at 0K. 
        }
        \label{fig:allmodels_no_strainphonon_b2}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotNoStrainPhonons.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/B19_combined_models_phonon_bandstructures.png}
        \caption{
          Ground-state phonon bandstructure of B19 phase for all models.
        }
        \label{fig:allmodels_no_strainphonon_B19P}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotNoStrainPhonons.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/B19P_combined_models_phonon_bandstructures.png}
        \caption{
          Ground-state phonon bandstructure of \textit{B19}$^\prime$ phase for all models.
        }
        \label{fig:allmodels_no_strainphonon_B19P}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotNoStrainPhonons.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/BCO_combined_models_phonon_bandstructures.png}
        \caption{
          Ground-state phonon bandstructure of BCO phase for all models.
        }
        \label{fig:allmodels_no_strainphonon_B19P}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotEAMPhonons.py}
    \begin{centering}
        \includegraphics[width=0.5\linewidth]{figures/Mutter_B2_combined_strain_phonon_bandstructures.png}
        \vspace{1mm}
        \includegraphics[width=0.5\linewidth]{figures/Zhong_B2_combined_strain_phonon_bandstructures.png}
        \caption{
           Phonon dispersion of B2 structure for the Mutter (top) and Zhong (bottom)  EAM potentials at different isotropic strains. The optical branches have been made more transparent to emphasis the behavior in the TA$_1$ and TA$_2$ branches. The color indicates direction from compressive to tensile strain. Note that the strain percent shown is with respect to isotropic changes (i.e. volume). 
        }
        \label{fig:mutter_zhong_phonon_b2}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \script{PlotGNNPhonons.py}
    \begin{centering}
      \includegraphics[width=0.5\linewidth]{figures/M3GNet_B2_combined_strain_phonon_bandstructures.png}
      \vspace{1mm}
      \includegraphics[width=0.5\linewidth]{figures/CHGNet_B2_combined_strain_phonon_bandstructures.png}
      \vspace{1mm}
      \includegraphics[width=0.5\linewidth]{figures/MACE_B2_combined_strain_phonon_bandstructures.png}
      \caption{
        Phonon dispersion of B2 structure for the (a) M3GNet, (b) CHGNet, and (c) MACE potentials for different isotropic strains. Similar transcparency is used as done in \ref{fig:mutter_zhong_phonon_b2}.
      }
      \label{fig:gnn_phonon_b2}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]                                                                                      
    \script{AppendixPlotBZ.py}                                                                           
    \begin{centering}                                                                                    
      \includegraphics[width=0.5\linewidth]{figures/B2_BrillouinZonePointsSampled.png} 
      \vspace{1mm}                                                                                       
      \includegraphics[width=0.5\linewidth]{figures/B19_BrillouinZonePointsSampled.png}
      \vspace{1mm}
      \includegraphics[width=0.5\linewidth]{figures/BCO_BrillouinZonePointsSampled.png}
      \vspace{1mm}                                                                                       
      \caption{The irreducible Brillouin zones for (top) B2(\#221) (middle) B19/B19P(\#11), and (bottom) BCO(\#63) crystal structures}                                                                                  \label{fig:ibz}                                                                          
    \end{centering}                                                                                      
\end{figure}

>>>>

\begin{figure}[ht!]
    \script{PlotCohesiveEnergy.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_CohesiveEnergyPlot.png}
        \caption{
          Comparison of predicted cohesive energy for respective ground-state structure and model.
        }
        \label{fig:ecoh}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotEOS.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_EquationOfStates.png}
        \caption{
            The equation of state curves for different \ce{NiTi} structures for (a) Mutter (EAM) (b) Zhong (EAM) (c) M3GNet (d) CHGNet (e) MACE and (f) ALIGNN interatomic potentials. The x-axis is the ratio of the isotropic strained unit cell volume, $V$,  with respect to the ground-state unit cell volume, $V_o$.
        }
        \label{fig:eos}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \script{PlotPhonons.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_B2_ModelsPhononBandstructures.png}
        \caption{
          Ground-state, no isotropic strain, Phonon bandstructure of B2 phase for all models. The Mutter and Zhong EAM potentials differ in that Mutter predicts no dynamic instability of the B2 phase at 0K. 
        }
        \label{fig:allmodels_b2}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotPhonons.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_B19_ModelsPhononBandstructures.png}
        \caption{
          Ground-state phonon bandstructure of B19 phase for all models.
        }
        \label{fig:allmodels_B19P}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotPhonons.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_B19P_ModelsPhononBandstructures.png}
        \caption{
          Ground-state phonon bandstructure of \textit{B19}$^\prime$ phase for all models.
        }
        \label{fig:allmodels_B19P}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotPhonons.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_BCO_ModelsPhononBandstructures.png}
        \caption{
          Ground-state phonon bandstructure of BCO phase for all models.
        }
        \label{fig:allmodels_B19P}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotEAMPhonons.py}
    \begin{centering}
        \includegraphics[width=0.5\linewidth]{figures/NiTi_Mutter_B2_StrainsPhononBandstructures.png}
        \vspace{1mm}
        \includegraphics[width=0.5\linewidth]{figures/NiTi_Zhong_B2_StrainsPhononBandstructures.png}
        \caption{
           Phonon dispersion of B2 structure for the Mutter (top) and Zhong (bottom)  EAM potentials at different isotropic strains. The optical branches have been made more transparent to emphasis the behavior in the TA$_1$ and TA$_2$ branches. The color indicates direction from compressive to tensile strain. Note that the strain percent shown is with respect to isotropic changes (i.e. volume). 
        }
        \label{fig:mutter_zhong_phonon_b2}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \script{PlotGNNPhonons.py}
    \begin{centering}
      \includegraphics[width=0.5\linewidth]{figures/NiTi_M3GNet_B2_StrainsPhononBandstructures.png}
      \vspace{1mm}
      \includegraphics[width=0.5\linewidth]{figures/NiTi_CHGNet_B2_StrainsPhononBandstructures.png}
      \vspace{1mm}
      \includegraphics[width=0.5\linewidth]{figures/NiTi_MACE_B2_StrainsPhononBandstructures.png}
      \caption{
        Phonon dispersion of B2 structure for the (a) M3GNet, (b) CHGNet, and (c) MACE potentials for different isotropic strains. Similar transcparency is used as done in \ref{fig:mutter_zhong_phonon_b2}.
      }
      \label{fig:gnn_phonon_b2}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]                                                                                      
    \script{AppendixBZ.py}                                                                           
    \begin{centering}                                                                                    
      \includegraphics[width=0.5\linewidth]{figures/B2_BrillouinZonePointsSampled.png} 
      \vspace{1mm}                                                                                       
      \includegraphics[width=0.5\linewidth]{figures/B19_BrillouinZonePointsSampled.png}
      \vspace{1mm}
      \includegraphics[width=0.5\linewidth]{figures/BCO_BrillouinZonePointsSampled.png}
      \vspace{1mm}                                                                                       
      \caption{The irreducible Brillouin zones for (top) B2(\#221) (middle) B19/B19P(\#11), and (bottom) BCO(\#63) crystal structures}                                                                                  \label{fig:ibz}                                                                          
    \end{centering}                                                                                      
\end{figure}
